---
title: "SEER Sigmoidoscopy Project"
author: "david.hein@utsouthwestern.edu"
date: "`r Sys.Date()`"
format: 
    html: 
        toc: true
        number_sections: true
        fig-width: 6
        fig-height: 3
  gfm:
      toc: true
      number_sections: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Load packages and raw data
```{r, results = 'hide', message = FALSE, warning = FALSE}
library(broom)
library(MASS)
library(survival)
library(survminer)
library(tidyverse)
library(survRM2)
library(km.ci)
library(readr)
library(table1)
library(epitools)
library(riskRegression)
library(adjustedCurves)
set.seed(2023)
seer_data <- read_delim("SEERdata42623.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
```




# Data cleaning
```{r}
# Get only variables we want
new_data <- seer_data %>% dplyr::select(Sex, `Year of diagnosis`,
                                `Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic) - no total`,
                                `Primary Site`,`Grade Recode (thru 2017)`,
                                `Grade Pathological (2018+)`,
                                `Combined Summary Stage (2004+)`,
                                `Summary stage 2000 (1998-2017)`,
                                `SEER cause-specific death classification`,
                                `Survival months`,
                                `Age recode with single ages and 90+`,
                                `Survival months flag`,
                                `Vital status recode (study cutoff used)`,
                                `Grade Clinical (2018+)`,
                                `Histologic Type ICD-O-3`,
                                `COD to site recode ICD-O-3 2023 Revision`,
                                `SEER other cause of death classification`,
                                `Site recode ICD-O-3/WHO 2008`)

# need to take out 181 appendix, 260, 188, and 189 because location unknown
new_data <- new_data %>% 
  filter(!`Primary Site` %in% c(260, 188, 189, 181))

# only adenocarcinoma
new_data <- new_data %>% 
  filter(`Histologic Type ICD-O-3`== 8140)

# make a new variable for site being seen on colonsocopy or sigmoid, should include 186 descending, 187 sigmoid, 199 rectosigmoid junction, 209 rectum NOS
new_data <- new_data %>% 
  mutate(can_see_sigmoid = ifelse( `Primary Site` %in% c(186, 187, 199, 209), 1, 0))

# make new variable for 3 age groups
new_data <- new_data %>%
  mutate(age_numeric = as.numeric(str_extract(`Age recode with single ages and 90+`, "[:digit:]+")))
new_data <- new_data %>% 
  mutate(age_group_final = ifelse(age_numeric <44,'under45', 'over50'))%>%
  mutate(age_group_final = ifelse(age_numeric <53 & age_numeric >= 44, '45-50', age_group_final))

# Combine the two stages
new_data <- new_data %>% 
  mutate(new_stage = ifelse(`Summary stage 2000 (1998-2017)` == "Blank(s)",
                            `Combined Summary Stage (2004+)`,
                            `Summary stage 2000 (1998-2017)`))

# Filter out unknown stage an in situ
new_data2 <- new_data %>% 
  filter( !new_stage %in%c("Unknown/unstaged", "In situ"))

# Make nice grade variable from different grade styles
new_data2 <- new_data2 %>% 
  mutate(final_grade = `Grade Pathological (2018+)`)

new_data2 <- new_data2 %>% 
  mutate(final_grade = ifelse(`Grade Recode (thru 2017)` %in% "Poorly differentiated; Grade III", "3", final_grade))

new_data2 <- new_data2 %>% 
  mutate(final_grade = ifelse(`Grade Recode (thru 2017)` %in% "Undifferentiated; anaplastic; Grade IV", "4", final_grade))

new_data2 <- new_data2 %>% 
  mutate(final_grade = ifelse(`Grade Recode (thru 2017)` %in% "Moderately differentiated; Grade II", "2", final_grade))

new_data2 <- new_data2 %>% 
  mutate(final_grade = ifelse(`Grade Recode (thru 2017)` %in% "Well differentiated; Grade I", "1", final_grade))

# toss em in an unknown/other
new_data2 <- new_data2 %>% 
  mutate(final_grade = ifelse(final_grade %in% c("A", "B", "Blank(s)", "L","C", "H", "9", "D"), "unk_other", final_grade))

# make smaller year of diagnosis groups
new_data2 <- new_data2 %>% 
              mutate(year_of_diag = case_when(
                `Year of diagnosis`%in%c('2000', '2001', '2002' ,'2003' ,'2004') ~ "yod1",
                `Year of diagnosis`%in%c('2005','2006', '2007', '2008' ,'2009') ~ "yod2",
                `Year of diagnosis`%in%c('2010', '2011', '2012' ,'2013' ,'2014') ~ "yod3",
                `Year of diagnosis`%in%c('2015', '2016', '2017' ,'2018' ,'2019','2020') ~ "yod4"))

# make cleaner race/eth column name
new_data2 <- new_data2 %>% 
  rename(race_eth=`Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic) - no total`)

# Survival
# CSS
new_data3 <- new_data2 %>% 
  mutate(cancer_specific_status = case_when(
    `COD to site recode ICD-O-3 2023 Revision`=="Alive"~0,
    `SEER cause-specific death classification`=="Dead (attributable to this cancer dx)"~1,
    `SEER other cause of death classification`=="Dead (attributable to causes other than this cancer dx)"~2,
    `SEER cause-specific death classification`=="Dead (missing/unknown COD)"~2))

# OS
new_data3 <- new_data3 %>% 
  mutate(overall_status = ifelse(`Vital status recode (study cutoff used)`=="Alive", 0, 1 ))

new_data4 <- new_data3 %>% 
  filter(`Survival months flag`=='Complete dates are available and there are more than 0 days of survival')

# Remove old data sets to save space
rm(seer_data)
rm(new_data)
rm(new_data2)
rm(new_data3)

#######################################################################
#table(new_data4$cancer_specific_status, useNA = "always")
```





# Setting reference groups
Makes this easier for filling out tables and for regressions
```{r}
# first select only variables we know we will be using to save space
new_data5<-new_data4 %>% dplyr::select(Sex,
                                       race_eth,
                                       can_see_sigmoid,
                                       age_group_final,
                                       new_stage, 
                                       final_grade,
                                       year_of_diag,
                                       cancer_specific_status, 
                                       overall_status,
                                       `Survival months`,
                                       `Primary Site`,
                                       age_numeric,
                                       `Site recode ICD-O-3/WHO 2008`)%>%
                          rename(survival_months=`Survival months`, primary_site = `Primary Site`)

# set new factor levels, first level is the reference group
new_data5$new_stage <- factor(new_data5$new_stage, levels = c('Localized', 'Regional', 'Distant'))
new_data5$age_group_final <- factor(new_data5$age_group_final, levels = c('over50', 'under45', '45-50'))
new_data5$year_of_diag <- factor(new_data5$year_of_diag, levels = c('yod1', 'yod2', 'yod3', 'yod4'))

# we dont need to specify all levels for race that would take too much typing, we just want to set the largest group as the reference
new_data5 <- within(new_data5, race_eth <- relevel(factor(race_eth), ref = 'Non-Hispanic White'))

# The grade variable appears to be unreliable
#table(new_data5$final_grade, new_data5$year_of_diag)

# now using new_data5
rm(new_data4)

# make sure surv months is numeric
new_data5 <- new_data5 %>% mutate(survival_months = as.numeric(`survival_months`))


# Print out table 1
#table(new_data5$primary_site,new_data5$age_group_final,new_data5$new_stage)

# Make a nice neat table 1
tbl1 <- new_data5 %>% dplyr::select(`Site recode ICD-O-3/WHO 2008`, new_stage, age_group_final)
tbl1$age_group_final <- factor(tbl1$age_group_final, levels = c('under45','45-50','over50'))
tbl1$`Site recode ICD-O-3/WHO 2008` <- factor(tbl1$`Site recode ICD-O-3/WHO 2008`, 
                                              levels = c("Rectum",
                                                         "Rectosigmoid Junction",
                                                         "Sigmoid Colon",
                                                         "Descending Colon",
                                                         "Splenic Flexure",
                                                         "Transverse Colon",
                                                         "Hepatic Flexure",
                                                         "Ascending Colon",
                                                         "Cecum"))

#table1(~ `Site recode ICD-O-3/WHO 2008` | new_stage*age_group_final, data = tbl1) this prints a pretty html version, to output in github doc we need to use kable
#knitr::kable(table1(~ `Site recode ICD-O-3/WHO 2008` | new_stage*age_group_final, data = tbl1))
table1(~ `Site recode ICD-O-3/WHO 2008` | new_stage*age_group_final, data = tbl1)
```




# Stacked Bar graph figure
```{r, warning=FALSE, message=FALSE}
# Group the 'new_data5' dataframe by 'age_numeric' and 'new_stage' and calculate the proportion
# of cases that can see a sigmoid.
sum_data <- new_data5 %>% 
  group_by(age_numeric, new_stage) %>% 
  summarize(sigcan = sum(can_see_sigmoid)/n())

# Calculate the proportion of cases that cannot see a sigmoid and store in a new column 'nocan'.
sum_data$nocan <- 1-sum_data$sigcan

# Reshape the dataframe from wide to long format, converting 'sigcan' and 'nocan' columns to 
# 'proptype' and 'proportion' columns.
sum_data <- pivot_longer(sum_data, cols = c(sigcan,nocan), names_to = "proptype", values_to = "proportion")

# Plot the data using ggplot2.
ggplot(sum_data, aes(x = age_numeric, y = proportion, fill = proptype)) +
  # Use bars to represent the data. The height of the bars indicates the proportion.
  geom_bar(stat = "identity", position="fill", width = 1.1) +
  # Split the plot into multiple panels based on the 'new_stage' column.
  facet_wrap(~ new_stage, ncol = 1) +
  # Use the 'test' theme for the plot. This theme provides a clean and minimalistic look.
  theme_test() +
  # Label the fill colors to indicate whether the sigmoid can or cannot be visualized.
  labs(fill = "Visualization on Sigmoidoscopy") +
  # Manually set the fill colors and their corresponding labels.
  scale_fill_manual(labels = c("Can NOT be visualized", "Can be visualized"), 
                    values = c("#f4a582", "#92c5de")) +
  # Label the y-axis and x-axis.
  ylab("Proportion of Total Cases") + xlab("Age at diagnosis") +
  # Set the limits and breaks for the x-axis.
  scale_x_continuous(limits = c(18,90), breaks = c(20, 30, 40, 45, 50, 60, 70, 80)) +
  # Add two vertical dashed lines at x = 44.5 and x = 49.5.
  geom_vline(aes(xintercept = 44.5), color = "black", linetype="dashed", size = 0.4) +
  geom_vline(aes(xintercept = 49.5), color = "black", linetype="dashed", size = 0.4)


#ggsave(plot=last_plot(),file="bar_graph.png", heigh=4, width=6,dpi = "retina")
#ggsave(plot=last_plot(),file="bar_graph.tiff", heigh=4, width=6)


```




# Logistic Regression 
Calculates odds of tumor in location seen on sigmoidoscopy, first univariate then multivariate
```{r}
# Code below calculates, exps, and does CI, then only saves the output to save space
sex_log<-tidy(glm(can_see_sigmoid~Sex,data=new_data5,family="binomial"),conf.int=TRUE)%>%
          mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))


sex_log<-glm(can_see_sigmoid~Sex,data=new_data5,family="binomial")


age_log<-tidy(glm(can_see_sigmoid~age_group_final,data=new_data5,family="binomial"),conf.int=TRUE)%>%
          mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

stage_log<-tidy(glm(can_see_sigmoid~new_stage,data=new_data5,family="binomial"),conf.int=TRUE)%>%
            mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

year_log<-tidy(glm(can_see_sigmoid~year_of_diag,data=new_data5,family="binomial"),conf.int=TRUE)%>%
            mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

race_log<-tidy(glm(can_see_sigmoid~race_eth,data=new_data5,family="binomial"),conf.int=TRUE)%>%
            mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

# Multivariate, Check out interactions
multi_log<-tidy(glm(can_see_sigmoid~race_eth+Sex+age_group_final+new_stage+year_of_diag,data=new_data5,family="binomial"),conf.int=TRUE)%>%
  mutate(estimate=exp(estimate),conf.low=exp(conf.low),conf.high=exp(conf.high))

propensity_log <- glm(can_see_sigmoid~race_eth+Sex,data=new_data5,family="binomial")
summary(propensity_log)


```




## Logistic results: sex
```{r}
knitr::kable(sex_log,digits=2)
```
## Logistic results: age
```{r}
knitr::kable(age_log,digits=2)
```
## Logistic results: stage
```{r}
knitr::kable(stage_log,digits=2)
```
## Logistic results: year
```{r}
knitr::kable(year_log,digits=2)
```
## Logistic results: race
```{r}
knitr::kable(race_log,digits=2)
```
## Logistic results: multivariate
```{r}
knitr::kable(multi_log,digits=2)
```




# Survival exploration w/OS
Makes KM curves using OS, checks proportional hazards assumptions

## KM plots: Can see on sigmoidoscopy 
```{r}
# CAN SEE
km_cansee<-survfit(Surv(survival_months, overall_status) ~ can_see_sigmoid, data = new_data5)
plot(km_cansee,fun="cloglog")
ggsurvplot(km_cansee,censor=FALSE) # BIGGEST TIME DEPENDANT!!!
```

## KM plots: Stage
```{r}
# STAGE
km_new_stage<-survfit(Surv(survival_months, overall_status) ~new_stage, data = new_data5)
plot(km_new_stage,fun="cloglog")
ggsurvplot(km_new_stage,censor=FALSE)
```

## KM plots: year of diag
```{r}
# YEAR OF DIAG
km_year_of_diag<-survfit(Surv(survival_months, overall_status) ~ year_of_diag, data = new_data5)
ggsurvplot(km_year_of_diag,censor=FALSE)
plot(km_year_of_diag,fun="cloglog")
```

## KM plots: sex
```{r}
# SEX
km_Sex<-survfit(Surv(survival_months, overall_status) ~ Sex, data = new_data5)
ggsurvplot(km_Sex,censor=FALSE)
plot(km_Sex,fun="cloglog") # lines cross but tiny
```

## KM plots: age group
```{r}
# AGE GROUP
km_age_group_final<-survfit(Surv(survival_months, overall_status) ~ age_group_final, data = new_data5)
ggsurvplot(km_age_group_final,censor=FALSE) # lines cross but tiny
plot(km_age_group_final,fun="cloglog") 
```

## KM plots: race_eth
```{r}
# RACE ETH
km_race_eth<-survfit(Surv(survival_months, overall_status) ~ race_eth, data = new_data6)
ggsurvplot(km_race_eth,censor=FALSE) # lines cross but insignificant 
plot(km_race_eth,fun="cloglog") 
table(new_data5$race_eth)
```

## KM plots: Site
```{r}
# SITE (this is just can see sigmoid with more definition)
km_site<-survfit(Surv(survival_months, overall_status) ~ primary_site, data = new_data5)
ggsurvplot(km_site,censor=FALSE,ylim=c(0.5,1),xlim=c(0,100))
#table(new_data5$primary_site)
```



# New way of calculating RMST
```{r}
# Define a function to compute the adjusted survival curve for a specific age group and stage.
get_adjusted_surv <- function(age_group, stage, osdata) {

  # Filter the input dataset based on the given age group and stage.
  # Select the relevant columns and recode the 'can_see_sigmoid' variable.
  os_surv_data <- osdata %>%
    filter(age_group_final == age_group, new_stage == stage) %>%
    select(can_see_sigmoid, survival_months, overall_status, race_eth, Sex) %>%
    mutate(can_see_sigmoid2 = as.factor(ifelse(can_see_sigmoid == 0, "not_see", "can_see")))

  # Fit a logistic regression model to estimate the propensity scores. 
  # The propensity score model predicts the probability of seeing sigmoid based on race and sex.
  propensity_log <- glm(can_see_sigmoid ~ race_eth + Sex, data = os_surv_data, family = "binomial")

  # Compute the adjusted survival curves using the inverse probability of treatment weighting (IPTW) method. 
  # The adjustment is done based on the propensity scores derived from the logistic regression model.
  surv_adjusted <- adjustedsurv(os_surv_data, 
                                variable = "can_see_sigmoid2", 
                                ev_time = "survival_months",
                                event = "overall_status", 
                                method = "iptw_km", 
                                treatment_model = propensity_log,
                                conf_int = TRUE, 
                                clean_data = TRUE, 
                                bootstrap = TRUE, 
                                n_boot = 2000, 
                                conf_level = 0.95, 
                                # May need to delete the n_cores line if computer crashes!
                                n_cores = 4)
  
  # Return the computed adjusted survival curve.
  return(surv_adjusted)
}


# View the documentation for the 'adjustedsurv' function.
?adjustedsurv

# Define a function to compute the restricted mean survival time (RMST) based on the adjusted survival curve.
get_rmst <- function(adj_surv, age_group, stage, months) {
  
  # Correct the significance level for multiple testing (27 tests).
  alpha_corrected <- 1-(0.05/27)

  # Compute the RMST for two groups ('not_see' and 'can_see') based on the adjusted survival curve.
  # CHANGE DIFFERENCE TO TRUE TO COMPUTE DIFFERENCE IN RMST
  rmst_results <- adjusted_rmst(adj_surv, 
                                to = months, 
                                difference = FALSE, 
                                conf_int = TRUE, 
                                group_1 = "not_see", 
                                group_2 = "can_see", 
                                conf_level = alpha_corrected)

  # Convert the RMST results to a data frame and add additional columns (age group, stage, and time point).
  rmst_tidy <- rmst_results %>%
    as.data.frame() %>%
    mutate(age_group = age_group, stage = stage, time_p = months)
  
  # Return the tidied RMST results.
  return(rmst_tidy)
}


# Get all adjusted curves, set seed for reproducibility 
ts <- Sys.time()
set.seed(2023)
surv_local_young <- get_adjusted_surv("under45","Localized", new_data6)
te <- Sys.time()
print(te-ts)
set.seed(2023)
surv_local_mid <- get_adjusted_surv("45-50","Localized", new_data6)
set.seed(2023)
surv_local_old <- get_adjusted_surv("over50","Localized", new_data6)
set.seed(2023)
surv_reg_young <- get_adjusted_surv("under45","Regional", new_data6)
set.seed(2023)
surv_reg_mid <- get_adjusted_surv("45-50","Regional", new_data6)
set.seed(2023)
surv_reg_old <- get_adjusted_surv("over50","Regional", new_data6)
set.seed(2023)
surv_dist_young <- get_adjusted_surv("under45","Distant", new_data6)
set.seed(2023)
surv_dist_mid <- get_adjusted_surv("45-50","Distant", new_data6)
set.seed(2023)
surv_dist_old <- get_adjusted_surv("over50","Distant", new_data6)




# Create a list of adjusted survival curve objects.
# These objects likely represent survival curves for different combinations of age groups and disease stages.
survs <- list(surv_local_young, surv_local_mid, surv_local_old, 
              surv_reg_young, surv_reg_mid, surv_reg_old, 
              surv_dist_young, surv_dist_mid, surv_dist_old)

# Initialize an empty data frame to store the results from the RMST calculations.
all_rmsts <- data.frame()

# Define the disease stages and age groups as vectors.
stages <- c("Localized","Regional","Distant")
ages <- c("under45", "45-50", "over50")

# Initialize a counter 'i' to keep track of the current iteration.
i <- 0

# Loop through each adjusted survival curve object in the 'survs' list.
for (surv in survs) {
  
  # For each survival curve object, calculate the RMST at 3 specific time points: 24, 60, and 120 months.
  for (m in c(24,60,120)) {
    # Call the 'get_rmst' function to compute the RMST for the current survival curve object, 
    # corresponding age group, and disease stage at the time point 'm'.
       # Using modulo arithmetic to cyclically select age groups in the order "under45", "45-50", "over50".
       # for i=0,1,2,3,4,5,…, the expression i %% 3 will yield 0, 1, 2, 0, 1, 2 etc.
       # Using ceiling to round up values to switch disease states every 3 iterations
       # for i=0,1,2,3,4,5,…, the expression ceiling((i+1)/3) will yield 0.33,0.67,1,1.33,1.67,2 etc.
    # Append the resulting data frame to the 'all_rmsts ' data frame.
    all_rmsts  <- rbind(all_rmsts , get_rmst(surv, ages[1 + i %% 3], stages[ceiling((i+1)/3)], m))
  }
  
  # Increment the counter 'i' for the next iteration.
  i <- i + 1
}

#write.table(deltas, "all_RMST.txt", sep="\t", row.names = FALSE, quote = FALSE)

```




# Survival Analysis 
```{r}
# Organize and recode the 'all_rmst' dataframe for plotting.
all_rmst2 <- all_rmst %>% 
  # Create a new variable 'color_var' combining 'group' and 'time_p' to determine colors in the plot.
  mutate(color_var = factor(paste0(group, as.character(time_p)), 
                            levels=c('not_see120','not_see60','not_see24','can_see120','can_see60','can_see24'))) %>%
  # Ensure proper ordering of the 'age_group' and 'stage' variables for the plot.
  mutate(age_group = factor(age_group, levels=c('under45','45-50','over50')),
         stage = factor(stage, levels=c('Distant','Regional','Localized'))) %>%
  # Filter out specific combinations of 'age_group', 'time_p', and 'stage'. 
    # Filtered out because there are not enough data points to accuratly asses confidence interval
  filter(!(age_group =="45-50" & time_p == 120 & stage=="Distant"))



# Recode age groups for better readability in the plot.
all_rmst3 <- all_rmst2 %>%
  mutate(group2 = case_when(
    age_group == "45-50" ~ "45-49",
    age_group == "under45" ~ "Under 45",
    age_group == "over50" ~ "Over 50"
  )) %>%
  mutate(group2 = factor(group2, levels=c('Under 45','45-49','Over 50')))


# Plotting the RMST data.
ggplot(data = all_rmst3, aes(y = rmst, x = stage, color = color_var, 
                             ymin = rmst-2.58*se, ymax = rmst+2.58*se, 
                             group = group)) + 
  # this is the specific geom that makes the graph
  geom_pointrange(position = position_dodge(width=0.5)) + 
  facet_wrap(~group2, ncol=1) + 
  scale_color_manual(
    labels = c("Requires Colonoscopy: 10 years", "Requires Colonoscopy: 5 years", "Requires Colonoscopy: 2 years",
               "Sigmoidoscopy: 10 years", "Sigmoidoscopy: 5 years", "Sigmoidoscopy: 2 years"), 
    values = c("#b2182b","#d6604d","#f4a582","#2166ac","#4393c3","#92c5de"),
    name = "Tumor location \nand RMST follow up time"
  ) + 
  coord_flip() + 
  scale_y_continuous(limits=c(0,122), breaks=c(0,24,60,120), labels=c("0","2","5","10")) + 
  theme_bw() + 
  theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_line(linetype = 2)) + 
  ylab("Years of Follow Up") + 
  xlab("")

# Save the generated plot as a TIFF image.
ggsave(plot = last_plot(), filename = "rmst_fig.tiff", width = 8, height = 6)


```




# KM Plots with better 95% CIs
```{r}
# takes in plot data generated from make_plot_dat plus a string as the fig title, returns ggplot object of KM plot
make_plot <- function(plot_dat,fig_title){
  
  plot_dat2 <- as.data.frame(plot_dat$adjsurv)
  
  p <- ggplot(plot_dat2 ,aes(x=time,y=surv,color=group))+
    geom_step()+
    # set custom y axis limits, might actually want to just have the at 0,1 for all graphs 
    ylim(if(str_detect(fig_title,"Distant")) c(0,1) else c(0,1))+
    geom_ribbon(aes(ymin=ci_lower,ymax=ci_upper,x=time,fill=group),alpha=.2,size=0.1)+
    ggtitle(fig_title)+theme_test()+
    theme(
      plot.title = element_text(size=12),
      axis.title = element_blank(),
      panel.grid.major.x = element_line(linewidth=0.2,linetype = 3)
      )+
    # x axis breaks at 2,5,10, and 15 years
    scale_x_continuous(limits=c(0,240),breaks=c(0,24,60,120,180),labels=c("0","2","5","10","15"))+
    labs(fill="Tumor Location",color="Tumor Location")+
    scale_fill_manual(labels= c("Can be seen on sigmoidoscopy", "Can NOT be seen on sigmoidoscopy"),values=c("#92c5de","#f4a582")) +
    scale_color_manual(labels= c("Can be seen on sigmoidoscopy", "Can NOT be seen on sigmoidoscopy"),values=c("#0571b0","#ca0020"))
    
  return(p)
}

#text = element_text(family = "Calibri")
```



## OS plots NEW
```{r,fig.width=9,fig.height=6}
# Local
a_os<-make_plot(surv_local_young,"A: <45 Local")

b_os<-make_plot(surv_local_mid,"B: 45-49 Local")

c_os<-make_plot(surv_local_old ,"C: 50+ Local")


# Regional
d_os<-make_plot(surv_reg_young,"D: <45 Regional")

e_os<-make_plot(surv_reg_mid,"E: 45-49 Regional")

f_os<-make_plot(surv_reg_old,"F: 50+ Regional")


# Distant
g_os<-make_plot(surv_dist_young,"G:<45 Distant")

h_os<-make_plot(surv_dist_mid ,"H: 45-49 Distant")

i_os<-make_plot(surv_dist_old ,"I: 50+ Distant")

# combine and arrage all plots in a single fig
ggarrange(a_os,b_os,c_os,d_os,e_os,f_os,g_os,h_os,i_os,common.legend = TRUE, legend = "bottom")

ggsave(plot=last_plot(),file="os_km2.tiff",height=8, width=11.5)

```


# Session Info
```{r}
sessionInfo()
```


