---
title: "SEER Sigmoidoscopy Project"
author: "david.hein@utsouthwestern.edu"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
<br>

# Load packages and raw data
```{r,results='hide',message=FALSE, warning=FALSE}
library(broom)
library(MASS)
library(survival)
library(survminer)
library(tidyverse)

library(survRM2)
library(km.ci)
set.seed(2023)

seer_data <- read_delim("seer_data.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
```
<br>


# Data cleaning
```{r}
# Get only variables we want
new_data<-seer_data%>%dplyr::select(Sex, `Year of diagnosis`,
                                `Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic)`,
                                `Primary Site`,`Grade (thru 2017)`,
                                `Grade Pathological (2018+)`,
                                `Combined Summary Stage (2004+)`,
                                `Summary stage 2000 (1998-2017)`,
                                `SEER cause-specific death classification`,
                                `Survival months`,
                                `Age recode with single ages and 100+`,
                                `Survival months flag`,
                                `Vital status recode (study cutoff used)`,
                                `Grade Clinical (2018+)`,
                                `Histologic Type ICD-O-3`)

# need to take out 181 appendix, 260, 188, and 189 becuase location unknown
new_data <-new_data %>% filter( !`Primary Site` %in% c(260,188,189,181))

# only adenocarcinoma
new_data <- new_data %>%filter(`Histologic Type ICD-O-3`==8140)

# make a new variable for site being seen on colonsocopy or sigmoid, should include 186 descending, 187 sigmoid, 199 rectosigmoid junction, 209 rectum NOS
new_data <- new_data %>% mutate(can_see_sigmoid = ifelse( `Primary Site` %in% c(186,187,199,209),1,0))

# make new variable for 3 age groups
new_data <- new_data %>% mutate(age_group = as.numeric(str_sub(`Age recode with single ages and 100+`,1,2)))
new_data <- new_data %>% mutate(age_group_final = ifelse(age_group <45,'under45', 'over50'))%>%
  mutate(age_group_final = ifelse(age_group <50 & age_group >= 45,'45-50',age_group_final))

# Combine the two stages
new_data<-new_data%>%mutate(new_stage = ifelse(`Summary stage 2000 (1998-2017)`=="Blank(s)",
                                               `Combined Summary Stage (2004+)`,`Summary stage 2000 (1998-2017)`))

# Filter out unknown stage an in situ
new_data2 <-new_data %>% filter( !new_stage %in%c("Unknown/unstaged","In situ"))

# Make nice grade variable
new_data2 <- new_data2 %>% mutate(final_grade = `Grade Pathological (2018+)`)
new_data2 <- new_data2 %>% mutate(final_grade = ifelse(`Grade (thru 2017)` %in% "Poorly differentiated; Grade III", "3", final_grade))
new_data2 <- new_data2 %>% mutate(final_grade = ifelse(`Grade (thru 2017)` %in% "Undifferentiated; anaplastic; Grade IV", "4", final_grade))
new_data2 <- new_data2 %>% mutate(final_grade = ifelse(`Grade (thru 2017)` %in% "Moderately differentiated; Grade II", "2", final_grade))
new_data2 <- new_data2 %>% mutate(final_grade = ifelse(`Grade (thru 2017)` %in% "Well differentiated; Grade I", "1", final_grade))

# toss em in an unknown/other
new_data2 <- new_data2 %>% mutate(final_grade = ifelse(final_grade%in%c("A", "B", "Blank(s)", "L","C", "H", "9","D"),"unk_other",final_grade))

# make smaller year of diagnosis groups
new_data2 <- new_data2 %>% mutate(year_of_diag = case_when(`Year of diagnosis`%in%c('2000', '2001', '2002' ,'2003' ,'2004') ~ "yod1",
                                                            `Year of diagnosis`%in%c('2005','2006', '2007', '2008' ,'2009') ~ "yod2",
                                                            `Year of diagnosis`%in%c('2010', '2011', '2012' ,'2013' ,'2014') ~ "yod3",
                                                            `Year of diagnosis`%in%c('2015', '2016', '2017' ,'2018' ,'2019') ~ "yod4"))

# make cleaner race/eth column name
new_data2<- new_data2%>%rename(race_eth=`Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic)`)

# Survival
new_data3<-new_data2%>% mutate(cancer_specific_status = ifelse(`SEER cause-specific death classification`=="Dead (attributable to this cancer dx)",1,0 ))
new_data3<-new_data3%>% mutate(overall_status = ifelse(`Vital status recode (study cutoff used)`=="Alive",0,1 ))
new_data4<-new_data3%>%filter(`Survival months flag`=='Complete dates are available and there are more than 0 days of survival')

# Remove old data sets to save space
rm(seer_data)
rm(new_data)
rm(new_data2)
rm(new_data3)
```
<br>


# Setting reference groups
Makes this easier for filling out tables and for regressions
```{r}
# first select only variables we know we will be using to save space
new_data5<-new_data4 %>% dplyr::select(Sex,
                                       race_eth,
                                       can_see_sigmoid,
                                       age_group_final,
                                       new_stage, 
                                       final_grade,
                                       year_of_diag,
                                       cancer_specific_status, 
                                       overall_status,
                                       `Survival months`,
                                       `Primary Site`)%>%
                          rename(survival_months=`Survival months`, primary_site = `Primary Site`)

# set new factor levels, first level is the reference group
new_data5$new_stage <- factor(new_data5$new_stage, levels = c('Localized','Regional','Distant'))
new_data5$age_group_final <- factor(new_data5$age_group_final, levels = c('over50','under45','45-50'))
new_data5$year_of_diag <- factor(new_data5$year_of_diag, levels = c('yod1','yod2','yod3','yod4'))

# we dont need to specify all levels for race that would take too much typing, we just want to set the largest group as the reference
new_data5 <- within(new_data5, race_eth <- relevel(factor(race_eth), ref = 'Non-Hispanic White'))

# The grade variable appears to be unreliable
table(new_data5$final_grade,new_data5$year_of_diag)

# now using new_data5
rm(new_data4)

# Print out table 1
table(new_data5$primary_site,new_data5$age_group_final,new_data5$new_stage)
```
<br>


# Logistic Regression 
Calculates odds of tumor in location seen on sigmoidoscopy, first univariate then multivariate
```{r}
# Code below calculates, exps, and does CI, then only saves the output to save space

sex_log<-tidy(glm(can_see_sigmoid~Sex,data=new_data5,family="binomial"),conf.int=TRUE)%>%
          mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

age_log<-tidy(glm(can_see_sigmoid~age_group_final,data=new_data5,family="binomial"),conf.int=TRUE)%>%
          mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

stage_log<-tidy(glm(can_see_sigmoid~new_stage,data=new_data5,family="binomial"),conf.int=TRUE)%>%
            mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

year_log<-tidy(glm(can_see_sigmoid~year_of_diag,data=new_data5,family="binomial"),conf.int=TRUE)%>%
            mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

race_log<-tidy(glm(can_see_sigmoid~race_eth,data=new_data5,family="binomial"),conf.int=TRUE)%>%
            mutate(estimate=exp(estimate), conf.low=exp(conf.low), conf.high=exp(conf.high))

# Multivariate, Check out interactions
multi_log<-tidy(glm(can_see_sigmoid~race_eth+Sex+age_group_final+new_stage+year_of_diag,data=new_data5,family="binomial"),conf.int=TRUE)%>%
  mutate(estimate=exp(estimate),conf.low=exp(conf.low),conf.high=exp(conf.high))

```
<br>


## Logistic results: sex
```{r}
knitr::kable(sex_log,digits=3)
```
## Logistic results: age
```{r}
knitr::kable(age_log,digits=3)
```
## Logistic results: stage
```{r}
knitr::kable(stage_log,digits=3)
```
## Logistic results: year
```{r}
knitr::kable(year_log,digits=3)
```
## Logistic results: race
```{r}
knitr::kable(race_log,digits=3)
```
## Logistic results: multivariate
```{r}
knitr::kable(multi_log,digits=3)
```
<br>



# Survival exploration w/CSS
Makes KM curves using CSS, checks proportional hazards assumptions

## KM plots: Can see on sigmoidoscopy 
```{r}
# CAN SEE
km_cansee<-survfit(Surv(survival_months, cancer_specific_status) ~ can_see_sigmoid, data = new_data5)
plot(km_cansee,fun="cloglog")
ggsurvplot(km_cansee,censor=FALSE) # BIGGEST TIME DEPENDANT!!!
```

## KM plots: Stage
```{r}
# STAGE
km_new_stage<-survfit(Surv(survival_months, cancer_specific_status) ~new_stage, data = new_data5)
plot(km_new_stage,fun="cloglog")
```

## KM plots: year of diag
```{r}
# YEAR OF DIAG
km_year_of_diag<-survfit(Surv(survival_months, cancer_specific_status) ~ year_of_diag, data = new_data5)
ggsurvplot(km_year_of_diag,censor=FALSE)
plot(km_year_of_diag,fun="cloglog")
```

## KM plots: sex
```{r}
# SEX
km_Sex<-survfit(Surv(survival_months, cancer_specific_status) ~ Sex, data = new_data5)
ggsurvplot(km_Sex,censor=FALSE)
plot(km_Sex,fun="cloglog") # lines cross but tiny
```

## KM plots: age group
```{r}
# AGE GROUP
km_age_group_final<-survfit(Surv(survival_months, cancer_specific_status) ~ age_group_final, data = new_data5)
ggsurvplot(km_age_group_final,censor=FALSE) # lines cross but tiny
plot(km_age_group_final,fun="cloglog") 
```

## KM plots: race/eth
```{r}
# RACE ETH
km_race_eth<-survfit(Surv(survival_months, cancer_specific_status) ~ race_eth, data = new_data5)
ggsurvplot(km_race_eth,censor=FALSE) # lines cross but insignificant 
plot(km_race_eth,fun="cloglog") 
```

## KM plots: Site
```{r}
# SITE (this is just can see sigmoid with more definition)
km_site<-survfit(Surv(survival_months, cancer_specific_status) ~ primary_site, data = new_data5)
ggsurvplot(km_site,censor=FALSE,ylim=c(0.5,1),xlim=c(0,100))
#table(new_data5$primary_site)
```
<br>



# Survival Analysis 
```{r}
# take out patients with 0 survival months
new_data6<-new_data5%>%filter(survival_months>0)
new_data7<- new_data6%>%select(survival_months,cancer_specific_status,can_see_sigmoid,age_group_final,new_stage,overall_status)

# computes rmst with age group as a covariate, takes dataframe, vector of time points, and the stage as inputs, returns a dataframe with results across time points in columns, rows are the stats we are looking at (add option to switch to OS)
compute_rmst_with_age <- function(data,time_points,stage,css=TRUE){
  
  data<-data %>% filter(new_stage==stage)
  covs<-model.matrix(~age_group_final,data=data)[,2:3]
  
  rms_combined <- data.frame(col1="rmst")
  
  for (t in time_points){
    # calcs rmst with alpha corrected for 3 stages and number of time points 
    if (css) {
       rms_temp <- rmst2(time=data$survival_months,status=data$cancer_specific_status,arm=data$can_see_sigmoid,covariates=covs,tau=t,alpha=0.05/(3*length(time_points)) )
    }else{
       rms_temp <- rmst2(time=data$survival_months,status=data$cancer_specific_status,arm=data$can_see_sigmoid,covariates=covs,tau=t,alpha=0.05/(3*length(time_points)) )
    }
   
    # round and add results to the data frame, each time point will be added as a block of columns 
    rms_temp_res <- data.frame(rms_temp$RMST.difference.adjusted) %>% select(-se.coef., -z ) %>% mutate_all((function(x) round(x,digits=3))) %>% setNames( paste0('m_',t,"_",names(.)) )
    rms_combined <- cbind(rms_combined,rms_temp_res)
  }
  
  return(rms_combined)
}


local_res_combined_css <- compute_rmst_with_age(new_data7,c(12,24,60,120),"Localized")
regional_res_combined_css <- compute_rmst_with_age(new_data7,c(12,24,60,120),"Regional")
distant_res_combined_css <- compute_rmst_with_age(new_data7,c(12,24,60,120),"Distant")

local_res_combined_os <- compute_rmst_with_age(new_data7,c(12,24,60,120),"Localized",FALSE)
regional_res_combined_os <- compute_rmst_with_age(new_data7,c(12,24,60,120),"Regional",FALSE)
distant_res_combined_os <- compute_rmst_with_age(new_data7,c(12,24,60,120),"Distant",FALSE)

knitr::kable(local_res_combined_css)
knitr::kable(regional_res_combined_css)
knitr::kable(distant_res_combined_css)

knitr::kable(local_res_combined_os)
knitr::kable(regional_res_combined_os)
knitr::kable(distant_res_combined_os)
```
<br><br>



# KM Plots with better 95% CIs
```{r}

# makes a KM fit and calcs logep 95% CIs, returns the data for use with ggplot
make_plot_dat <- function(data_set, age_grp, stage, css = TRUE){
  
  can <- data_set%>%filter(age_group_final==age_grp,new_stage==stage,can_see_sigmoid==1)
  nocan <- data_set%>%filter(age_group_final==age_grp,new_stage==stage,can_see_sigmoid==0)
  
  if (css){
    fit1 <- surv_fit(Surv(survival_months,cancer_specific_status)~1,data=can)
    fit2 <-  surv_fit(Surv(survival_months,cancer_specific_status)~1,data=nocan)
  }else{
    fit1 <- surv_fit(Surv(survival_months,overall_status)~1,data=can)
    fit2 <- surv_fit(Surv(survival_months,overall_status)~1,data=nocan)
  }
  
  fit1 <- km.ci(fit1,conf.level = 0.95,method = "logep")
  fit2 <- km.ci(fit2,conf.level = 0.95,method = "logep")
  
  pltdat1 <- as.data.frame(cbind(fit1$surv,fit1$time,fit1$n.risk,fit1$n.event,fit1$lower,fit1$upper))%>%mutate(type="cansee")
  pltdat2 <- as.data.frame(cbind(fit2$surv,fit2$time,fit2$n.risk,fit2$n.event,fit2$lower,fit2$upper))%>%mutate(type="cant see")
  
  colnames(pltdat1)<-c("surv","time","nrisk","nevent","lower","upper","type")
  colnames(pltdat2)<-c("surv","time","nrisk","nevent","lower","upper","type")

  plt3 <- rbind(pltdat1,pltdat2)
  return(plt3)
}

make_plot <- function(plot_dat,fig_title){# need to add in adjustment based on stage
  
  p <- ggplot(plot_dat ,aes(x=time,y=surv,color=type))+
    geom_step()+
    ylim(if(str_detect(fig_title,"Distant")) c(0,1) else c(0,1))+
    geom_ribbon(aes(ymin=lower,ymax=upper,x=time,fill=type),alpha=.1,size=0.2)+
    ggtitle(fig_title)+theme_test()+
    theme(
      plot.title = element_text(size=8),
      axis.title = element_blank()
      )+
    scale_x_continuous(limits=c(0,240),breaks=c(0,24,60,120,180),labels=c("0","2","5","10","15"))
  return(p)
}

```
<br><br>



# CSS Plots
```{r,fig.width=8,fig.height=6}

# Local
u45_local_plot <- make_plot_dat(new_data7, "under45", "Localized")
a<-make_plot(u45_local_plot,"A: <45 Local")

midage_local_plot <- make_plot_dat(new_data7, "45-50", "Localized")
b<-make_plot(midage_local_plot,"B: 45-50 Local")

o50_local_plot <- make_plot_dat(new_data7, "over50", "Localized")
c<-make_plot(o50_local_plot ,"C: >50 Local")


# Regional
u45_reg_plot <- make_plot_dat(new_data7, "under45", "Regional")
d<-make_plot(u45_reg_plot,"D: <45 Regional")

midage_reg_plot <- make_plot_dat(new_data7, "45-50", "Regional")
e<-make_plot(midage_reg_plot,"E: 45-50 Regional")

o50_reg_plot <- make_plot_dat(new_data7, "over50", "Regional")
f<-make_plot(o50_reg_plot,"F: >50 Regional")


# Distant
u45_dist_plot <- make_plot_dat(new_data7, "under45", "Distant")
g<-make_plot(u45_dist_plot,"G:<45 Distant")

midage_dist_plot <- make_plot_dat(new_data7, "45-50", "Distant")
h<-make_plot(midage_dist_plot ,"H: 45-50 Distant")

o50_dist_plot <- make_plot_dat(new_data7, "over50", "Distant")
i<-make_plot(o50_dist_plot ,"I: >50 Distant")

ggarrange(a,b,c,d,e,f,g,h,i,common.legend = TRUE)


ggsave(plot=last_plot(),file="css_km.png",height=8, width=11.5)

```
<br><br>



# OS plots
```{r,fig.width=8,fig.height=6}
# Local
u45_local_plot <- make_plot_dat(new_data7, "under45", "Localized",FALSE)
a<-make_plot(u45_local_plot,"A: <45 Local")

midage_local_plot <- make_plot_dat(new_data7, "45-50", "Localized",FALSE)
b<-make_plot(midage_local_plot,"B: 45-50 Local")

o50_local_plot <- make_plot_dat(new_data7, "over50", "Localized",FALSE)
c<-make_plot(o50_local_plot ,"C: >50 Local")


# Regional
u45_reg_plot <- make_plot_dat(new_data7, "under45", "Regional",FALSE)
d<-make_plot(u45_reg_plot,"D: <45 Regional")

midage_reg_plot <- make_plot_dat(new_data7, "45-50", "Regional",FALSE)
e<-make_plot(midage_reg_plot,"E: 45-50 Regional")

o50_reg_plot <- make_plot_dat(new_data7, "over50", "Regional",FALSE)
f<-make_plot(o50_reg_plot,"F: >50 Regional")


# Distant
u45_dist_plot <- make_plot_dat(new_data7, "under45", "Distant",FALSE)
g<-make_plot(u45_dist_plot,"G:<45 Distant")

midage_dist_plot <- make_plot_dat(new_data7, "45-50", "Distant",FALSE)
h<-make_plot(midage_dist_plot ,"H: 45-50 Distant")

o50_dist_plot <- make_plot_dat(new_data7, "over50", "Distant",FALSE)
i<-make_plot(o50_dist_plot ,"I: >50 Distant")

ggarrange(a,b,c,d,e,f,g,h,i,common.legend = TRUE)+ggtitle("OS")


ggsave(plot=last_plot(),file="os_km.png",height=8, width=11.5)

```
<br><br>



# Session Info
```{r}
sessionInfo()
```